Optimal Parameter Selection in Markov State Models for Biomolecular Conformational Dynamics

### 2013-11-13 paper/paper2.tex
paper edits

\section{Introduction}
Protein dynamics are an essential aspect of biomolecular function. These dynamics span a wide range of length scales, timescales and complexity, including folding and aggregation, the conformational change between functional native substates, ligand binding, and allostery \cite{Dobson2003Protein, Kim2008Real, Austin1975Dynamics, Bahar2007Intrinsic}. Whereas classical experimental probes have often been interpreted in two-state frameworks, ensemble measurements with infcreasingly high temporal resolution as well as sensitive single molecule probes have uncovered a vast array of complex kinetics occurring via various pathways and with multiple intermediates \cite{Cosa2006Evidence, Zhang2011Direct}. But atomic-resolution structural characterization of these dynamics is often a Herculean challenge, particularly in dynamical settings -- as molecular probes like F\"{o}rster resonance energy transfer, small-angle x-ray scattering, and nuclear magnetic resonance techniques measure complex projections of the intrinsic structure, generally reporting simultaneously on many degrees of freedom\cite{Mertens2010Structural, Tzeng2011Protein}.

@@

\begin{figure}
\centering
\includegraphics[width=3in]{figs/mull_ww.png}
\caption{Three systems studied in this work. (a) Langevin dynamics on the two dimensional M\"{u}ller potential. (b) 200 $\mu s$ of dynamics of the Fip35 WW domain\cite{Liu2008Experimental}, courtesy of D.E. Shaw research \cite{Shaw2010Atomic}.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=3.3in]{figs/mull_cross.png}
\caption{In models built using between 50 and 1,000 states with the $k$-centers algorithm, the log likelihood function increased quickly and plateaued at approximately 300 states. There are many methods that can be used to test the transferability of an MSM. We've plotted the AIC, BIC, and cross-validation scores for the WW domain. These results indicate that, at least for this dataset, the BIC and AIC may penalize the number of states too heavily. \hl{See SI section: ``AIC vs BIC" for a discussion of the various methods in detail.}}
\label{fig:mullerlike}
\end{figure}

>>>>

\section{Introduction}
Protein dynamics are an essential aspect of biomolecular function. These dynamics span a wide range of length scales, timescales and complexity, including folding and aggregation, conformational change between functional native substates, ligand binding, and allostery \cite{Dobson2003Protein, Kim2008Real, Austin1975Dynamics, Bahar2007Intrinsic}. Whereas classical experimental probes have often been interpreted in two-state frameworks, ensemble measurements with increasingly high temporal resolution as well as sensitive single molecule probes have uncovered a vast array of complex kinetics \cite{Cosa2006Evidence, Zhang2011Direct}. But atomic-resolution structural characterization of these dynamics is often a Herculean challenge, particularly in dynamical settings -- as molecular probes like F\"{o}rster resonance energy transfer, small-angle x-ray scattering, and nuclear magnetic resonance techniques measure complex projections of the intrinsic structure, generally reporting simultaneously on many degrees of freedom\cite{Mertens2010Structural, Tzeng2011Protein}.

@@

\begin{figure}
\centering
\includegraphics[width=3in]{figs/mull_ww.png}
\caption{Systems studied in this work. (A) Langevin dynamics on the two dimensional M\"{u}ller potential. (b) 200 $\mu s$ of dynamics of the Fip35 WW domain\cite{Liu2008Experimental}, courtesy of D.E. Shaw research \cite{Shaw2010Atomic}.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=3.3in]{figs/mull_cross.png}
\caption{In models built using between 50 and 1,000 states with the $k$-centers algorithm, the log likelihood function increased quickly and plateaued at approximately 300 states. There are many methods that can be used to test the transferability of an MSM. We've plotted the AIC, BIC, and cross-validation scores for the M\"uller potential simulations. These results indicate that, at least for this dataset, the BIC and AIC may penalize the number of states too heavily. \hl{See SI section: ``AIC vs BIC" for a discussion of the various methods in detail.}}
\label{fig:mullerlike}
\end{figure}
